### 2021-08-03 paper/paper.tex
JC paper edits (#5)
* paper edits

* Update paper/ref.bib

Co-authored-by: Hendrik Ranocha <ranocha@users.noreply.github.com>

* Update paper/paper.tex

Co-authored-by: Hendrik Ranocha <ranocha@users.noreply.github.com>

* applying changes as discussed on the PR

Co-authored-by: Jesse Chan <jesse.chan@rice.edu>
Co-authored-by: Hendrik Ranocha <ranocha@users.noreply.github.com>
fix URL

We are broadly interested in simulation-focused scientific computing, in particular
in hyperbolic partial differential equations (PDEs), computational fluid dynamics (CFD),
and related problems. The focus of our research ranges from specific applications
in CFD to general multi-physics coupling strategies to the high-order numerical methods 
such simulations are built upon. In addition, we are academics and involved in teaching 
students in these areas of science. Thus, we would like to have a 
code that is
\begin{enumerate}
  \item extendable to be useful for research and development
  \item easy to apply/understand to be useful for students/collaborators
  \item fast enough to be useful beyond small toy problems
\end{enumerate}
Additionally, we are greedy\footnote{See \url{https://julialang.org/blog/2012/02/why-we-created-julia/}} 
and wish to include all these features within a single code.
Roughly one year of collaborative work has resulted in the current version of
\trixi\footnote{https://github.com/trixi-framework/Trixi.jl}, providing adaptive
high-order numerical simulations of hyperbolic partial differential equations (PDEs)
in Julia \cite{bezanson2017julia}. Starting as an experiment, we have been able
to reach more and more of our goals with \trixi.

@@

Due to Julia's package manager, the cost of using external dependencies is low
enough to not be a problem. Traditionally, many scientific simulation codes tend
to reduce the number of external dependencies as much as possible due to the
complexity of handling different versions and making everything work together.
Such an approach typically leads to significant code duplication. For example, many
CFD codes implement their own time integration methods, arguing that the spatial
part is much more complex \todo{should we cite something for this?}. While this is often true, it is still more efficient
in terms of human workload to be able to reuse existing implementations. This
allows expert on time integration methods to develop specialized algorithms and
implement them in open source software while practitioners or researchers focusing
on spatial semidiscretizations ca benefit immediately by changing only one line
of code. For example, optimized time integration methods were developed in
\cite{ranocha2021optimized} and implemented in OrdinaryDiffEq.jl. These methods
can be used with \trixi by changing a single line of code. In contrast, researchers
working without external dependencies would need to spend a day or two to digest
details before even beginning implementation. This additional overhead in developer
time makes it less likely that researchers would implement these methods in their own 
codes and benefit from recent algorithmic developments.

@@

Jesse Chan acknowledge support from the US National Science Foundation under 
awards DMS-1719818 and DMS-1943186. 
% References
\input{bib.tex}

>>>>

We are broadly interested in simulation-focused scientific computing, in particular
in hyperbolic partial differential equations (PDEs), computational fluid dynamics (CFD),
and related problems. The focus of our research ranges from specific applications
in CFD to general multi-physics coupling strategies to the high-order numerical methods 
such simulations are built upon. In addition, we are academics and involved in teaching 
students in these areas of science. Thus, we would like to have a 
code that is
\begin{enumerate}
  \item extendable to be useful for research and development
  \item easy to apply/understand to be useful for students/collaborators
  \item fast enough to be useful beyond small toy problems
\end{enumerate}
Additionally, we are greedy\footnote{See \url{https://julialang.org/blog/2012/02/why-we-created-julia/}} 
and wish to include all these features within a single code.
Roughly one year of collaborative work has resulted in the current version of
\trixi\footnote{\url{https://github.com/trixi-framework/Trixi.jl}}, providing adaptive
high-order numerical simulations of hyperbolic partial differential equations (PDEs)
in Julia \cite{bezanson2017julia}. Starting as an experiment, we have been able
to reach more and more of our goals with \trixi.

@@

Due to Julia's package manager, the cost of using external dependencies is low
enough to not be a problem. Traditionally, many scientific simulation codes tend
to reduce the number of external dependencies as much as possible due to the
complexity of handling different versions and making everything work together.
Such an approach typically leads to significant code duplication. For example, many
CFD codes implement their own time integration methods, arguing that the spatial
part is much more complex. While this is often true, it is still more efficient
in terms of human workload to be able to reuse existing implementations. This
allows expert on time integration methods to develop specialized algorithms and
implement them in open source software while practitioners or researchers focusing
on spatial semidiscretizations ca benefit immediately by changing only one line
of code. For example, optimized time integration methods were developed in
\cite{ranocha2021optimized} and implemented in OrdinaryDiffEq.jl. These methods
can be used with \trixi by changing a single line of code. In contrast, researchers
working without external dependencies would need to spend a day or two to digest
details before even beginning implementation. This additional overhead in developer
time makes it less likely that researchers would implement these methods in their own 
codes and benefit from recent algorithmic developments.

@@

Jesse Chan acknowledges support from the US National Science Foundation under 
awards DMS-1719818 and DMS-1943186. 
% References
\input{bib.tex}
